\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Senior Data Scientist \hfill 10-2019 --- Present}}
\subtext{Adevinta \hfill Paris, France}
\begin{zitemize}
\item Offer new Computer Vision projects to improve CSAT and quality of the
MP apps
\item Background Removal application for \href{https://www.leboncoin.fr/}{Leboncoin}
\item Ad Param Classification to make users put the ads faster and more correct.  
\item Improve CSAT and quality of the Marketplace applications by using the power of Data.
\item Applications of Semi-Supervised Learning approaches.
\item Use a Synthetic dataset to solve the GDPR issues.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Lead Data Scientist \hfill 12-2018 --- 10-2019}}
\subtext{Volt Lines \hfill Istanbul, Turkey}
\begin{zitemize}
\item Turn the company from the business-based approach to the data-driven-based approach. Introduce the SMACK stack \href{https://medium.com/@cenk.bircanoglu/an-overview-of-data-pipeline-at-volt-lines-3743e15038cc}{Blog Post}
\item Gamification to make drivers use the app.
\item Daily, weakly, and monthly reports.
\item Build an automated and intelligent routing for services.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Senior/Lead Data Scientist \hfill 07-2017 --- 12-2018}}
\subtext{Boyner Group \hfill Istanbul, Turkey}
\begin{zitemize}
\item 2\% better performance on Recommendation Engine than third-party
solutions.
\item Visual Search Application for fashion objects.
\item Accelerate new product entry to inventory by image-based tagging.
\item Offer better prices for related products using image similarity to
outclass the competitors.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Independent Consultant \hfill 11-2017 --- 05-2018}}
\subtext{Udacity \hfill Remote}
\begin{zitemize}
\item As a consultant to educational platform(s), such as Udacity, I utilize my
specialized knowledge in the field of Deep Learning and my strong
communication skills to provide project reviews and other student support.
\end{zitemize}

\subsection{{R\&D Engineer \hfill 03-2017 --- 07-2017}}
\subtext{Huawei Technologies \hfill Istanbul, Turkey}
\begin{zitemize}
\item Experiment on Learning to Rank problems for enterprise search data using Deep Learning solutions.
\end{zitemize}

\subsection{{Software Developer/Data Scientist \hfill 09-2013 --- 03-2017}}
\subtext{Sekom Software \hfill Istanbul, Turkey}
\begin{zitemize}
\item Data collection from network types of equipment and Basic Data Science-based solutions.
\item Scheduled workflows on Big Data Environment. (Apache Hadoop, Apache Pig, Apache Kafka, Hive..) 
\item Alert prediction on monitoring data.
\end{zitemize}

\subsection{{Software Developer \hfill 06-2011 --- 09-2013}}
\subtext{Freelance \hfill Istanbul, Turkey}
\begin{zitemize}
\item Web Applications mostly build on Django Framework.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}